Something about Performance, 2D Component of NEMO. (TBC)

### 2015-03-11 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
Add plot and text for comparison of 1- and 2-socket performance results

>>>>

Since NEMO and similar finite-difference codes tend to be
memory-bandwidth bound, we checked the sensitivity of our performance
results to this quantity by benchmarking using two sockets of Intel
Ivy Bridge ({\it i.e.} using a complete node of Archer). For this
configuration we ensured that threads were evenly shared over the two
sockets. The performance obtained for the $256^2$ case with the `early
SINGLE' version of the code is compared with the single-socket
performance in Figure~\ref{FIG_omp_2socks}. Surprisingly, doubling the
available memory bandwidth in this way has little effect on
performance - the two-socket performance figures track those from a
single socket very closely. The only realy difference in performance
is at 24 threads where, in addition to the difference in available
memory bandwidth, the single-socket configuration is using
hyperthreading while the two-socket case is not.  {\bf Have query in
  with Archer helpdesk on behaviour seen with Cray compiler here. Also
  would like to run 512 case on 2 sockets to see how it goes out to 48
  threads.}

\begin{figure}
\centering
\includegraphics[width=\picwidth]{1and2sockets}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d on one and two sockets of Intel Ivy Bridge. The 24-thread
  runs on a single socket used hyperthreading and the two-socket runs
  had the threads shared equally between the sockets.}
\label{FIG_omp_2socks}
\end{figure}
